Data Preparation, Integration and Cleaning

### 2018-05-09 scripts/3_data_prep.Rmd
Simplify code up to write section

  library(tidyverse)
  library(sf)
  library(geosphere)
  library(ggmap)
  library(multidplyr)
  # library(lubridate)
  # library(spdep)
  # library(maptools)
  # library(ggplot2)

@@

Determine which suburbs are represented in both datasets and trim to those observations

@@

    sub_str <- str_sf %>% 
      dplyr::select(suburb, -geometry) %>% 
      as.tibble() %>%
      dplyr::group_by(suburb) %>% 
      dplyr::summarize(count=n())

    sub_ltr <- ltr_sf %>% 
      dplyr::select(suburb, -geometry) %>% 
      as.tibble() %>%
      dplyr::group_by(suburb) %>% 
      dplyr::summarize(count=n())

@@

@@

   # Order the factors properly
   ltr_sf$geo_mrkt <- factor(ltr_sf$geo_mrkt,
                               levels=c('city-core', 'city', 'suburban',
                                        'rural', 'beach'))
   # Count Cleaning
   countCleaning('location')

@@

  # Nightly Rate plot
  str_plot <- ggplot(str_tdf, aes(x=med_rate)) +
    geom_density(fill=str_col, alpha=.8) +
    ylab('') +
    xlab('Nightly Rate') +
    ggtitle('Short Term Rentals') +
    scale_x_continuous(limits=c(0, 600)) +
    theme(axis.title.y=element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y=element_blank()) +
    theme(plot.title = element_text(hjust = 0.5))

@@

   # Add together for plotting
   rev_df <- bind_rows(str_tdf %>% 
                         dplyr::select(type, gross_revenue) %>%
                         dplyr::mutate(tenure = 'str'),
                       ltr_tdf %>%
                         tidyr::unnest() %>%
                         dplyr::select(type, gross_revenue) %>%
                         dplyr::mutate(tenure = 'ltr'))

   revdens <- ggplot(rev_df, 
                     aes(x=gross_revenue, fill=tenure, color=tenure)) +
    geom_density(alpha=.5) +
    scale_fill_manual(values=c(ltr_col, abb_col)) +
    scale_color_manual(values=c(ltr_col, abb_col)) +
    ggtitle('Annual Revenues by Tenure Type') +
    xlab('Annual Revenue') +
    scale_x_continuous(breaks=c(seq(0,60000, by=20000)),
                       labels=c('$0', '$20,000', '$40,000', '$60,000'))+
    theme(legend.position='bottom',
          legend.title = element_blank(),
          plot.title = element_text(hjust = 0.5),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.title.y=element_blank()) +
    coord_cartesian(xlim=c(0, 70000))

@@

   prevdens <- ggplot(prev_df, 
                     aes(x=gross_revenue, fill=tenure, color=tenure)) +
    geom_density(alpha=.5) +
    scale_fill_manual(values=c(ltr_col, abb_col)) +
    scale_color_manual(values=c(ltr_col, abb_col)) +
    ggtitle('Annual Revenues by Tenure Type') +
    xlab('Annual Revenue') +
    scale_x_continuous(breaks=c(seq(0,60000, by=20000)),
                       labels=c('$0', '$20,000', '$40,000', '$60,000'))+
    theme(legend.position='bottom',
          legend.title = element_blank(),
          plot.title = element_text(hjust = 0.5),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.title.y=element_blank()) +
    coord_cartesian(xlim=c(0, 70000))

@@

```{r revdensplot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
# 
#   png(file=paste0(fig.path, 'revdens.png'), width = 480, height = 380, 
#       bg='transparent')
#     
#     revdens
#   
#   dev.off()
#   
#   save(revdens, file=paste0(fig.path, 'revdens.RData'))
#   
#   ltr_df <- ltr_df[ltr_df$dom <= 180, ]
#   
#     countCleaning('revenue')
```

@@

#```{r locationmaps.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
# 
#   # Set submarket colors
#   
#   sm_col <- abb_col[c(1, 3, 6, 5, 2)]
# 
#   # Make map
# 
#   str.map <- ggplot() +
#     geom_polygon(data=subs, aes(x=long, y=lat, group=group), fill='white', color='grey70') +
#     geom_point(data=str_df, aes(x=longitude, y=latitude, color=geo.mrkt), size=.2,
#                alpha=.2) +
#     scale_color_manual(values=sm_col) +
#     scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
#     scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
#     xlab('') + ylab('')+
#     theme(legend.position = 'bottom',
#           legend.title = element_blank(),
#           plot.title = element_text(hjust = 0.5),
#           panel.grid.major = element_blank(),
#           panel.grid.minor = element_blank(),
#           panel.background = element_rect(fill = "white"),
#           axis.text.x = element_blank(),
#           axis.text.y = element_blank(),
#           axis.ticks = element_blank(),
#           axis.title.x=element_blank(),
#           axis.title.y=element_blank(),
#           panel.border = element_rect(colour = "black", fill=NA, size=1)) +
#     guides(colour = guide_legend(override.aes = list(size=3,
#                                                      alpha=1))) + 
#     ggtitle('Short-Term Rental Locations')+
#     theme(plot.title = element_text(hjust = 0.5))
#   
# ```
# 
# ```{r ltr.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
# 
#   # Make map
# 
#   ltr.map <- ggplot() +
#     geom_polygon(data=subs, aes(x=long, y=lat, group=group), fill='white', color='grey70') +
#     geom_point(data=ltr_df, aes(x=longitude, y=latitude, color=geo.mrkt), size=.1,
#                alpha=.1) +
#     scale_color_manual(values=sm_col) +
#     scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
#     scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
#     xlab('') + ylab('')+
#     theme(legend.position = 'bottom',
#           legend.title = element_blank(),
#           plot.title = element_text(hjust = 0.5),
#           panel.grid.major = element_blank(),
#           panel.grid.minor = element_blank(),
#           panel.background = element_rect(fill = "white"),
#           axis.text.x = element_blank(),
#           axis.text.y = element_blank(),
#           axis.ticks = element_blank(),
#           axis.title.x=element_blank(),
#           axis.title.y=element_blank(),
#           panel.border = element_rect(colour = "black", fill=NA, size=1)) +
#     guides(colour = guide_legend(override.aes = list(size=3,
#                                                      alpha=1))) + 
#     ggtitle('Long-Term Rental Locations')+
#     theme(plot.title = element_text(hjust = 0.5))
#   
# ```
# 
# ```{r loc.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.width=9}
#   
#   png(file=paste0(fig.path, 'str_locmap.png'), width = 680, height = 590, 
#       bg='transparent')
#      str.map
#   dev.off()
#   
#   png(file=paste0(fig.path, 'ltr_locmap.png'), width = 680, height = 590, 
#       bg='transparent')
#      ltr.map
#   dev.off()
# 
#   ggMultiPlots(str.map, ltr.map, cols=2)
#   
#   save(str.map, file=paste0(fig.path, 'strMap.RData'))
#   save(ltr.map, file=paste0(fig.path, 'ltrMap.RData'))
# 
# 
# ```
# 
# The chart below break down the relative frequency of short and long term rental properties across the five submarkets. 
# 
```{r smtype.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.width=9}

>>>>

  library(tidyverse)
  library(sf)
  library(geosphere)
  library(ggmap)
  library(multidplyr)
  library(tmap)

@@

Determine which suburbs are represented in both datasets and trim to those observations to suburbs with at least three transactions

@@

    sub_str <- str_sf %>% 
      dplyr::select(suburb, -geometry) %>% 
      as.tibble() %>%
      dplyr::group_by(suburb) %>% 
      dplyr::summarize(count=n()) %>%
      dplyr::filter(count >= 3 & 
                      suburb != 'Maddingley')

    sub_ltr <- ltr_sf %>% 
      dplyr::select(suburb, -geometry) %>% 
      as.tibble() %>%
      dplyr::group_by(suburb) %>% 
      dplyr::summarize(count=n()) %>%
      dplyr::filter(count >= 3 & 
                      suburb != 'Maddingley')

@@

Create a polygon of the new study area

```{r new_study_area, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}

  all_sf <- rbind(str_sf %>% 
                    rename(uniq_id = property_id),
                  ltr_sf %>%
                    rename(uniq_id = addr_id))
  ssub_sf <- sub_sf %>% filter(NAME_2006 %in% sub_all$suburb)

  all_ch <- st_buffer(st_convex_hull(st_union(ssub_sf)), .001)
  within_ch <- st_contains(all_ch, sub_sf$geometry)
  subs_within <- sub_sf[unlist(within_ch), ]
  study_area <- st_union(subs_within)
  plot(study_area)

@@

   # Order the factors properly
   ltr_sf$geo_mrkt <- factor(ltr_sf$geo_mrkt,
                               levels=c('city-core', 'city', 'suburban',
                                        'rural', 'beach'))

  ltr_tdf %>% 
    dplyr::mutate(geometry = NULL) %>%
    as.tibble()

  str_tdf %>% 
    dplyr::mutate(geometry = NULL) %>%
    as.tibble()

   # Count Cleaning
   countCleaning('location')

Finally we add the spatial data back onto the tabular data (filtering out those outside of the study area using an inner join).

```{r merge_spatial, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}

  str_tdf <- str_tdf %>%
    dplyr::inner_join(str_sf, 
                      by='property_id')

  ltr_tdf <- ltr_tdf %>%
    dplyr::inner_join(ltr_sf,
                      by='addr_id')

@@

  # Nightly Rate plot
  str_price <- ggplot(str_tdf, aes(x=med_rate)) +
    geom_density(fill=str_col, alpha=.8) +
    ylab('') +
    xlab('Nightly Rate') +
    ggtitle('Short Term Rentals') +
    scale_x_continuous(limits=c(0, 600)) +
    theme(axis.title.y=element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y=element_blank()) +
    theme(plot.title = element_text(hjust = 0.5))

@@

   # Add together for plotting
   rev_df <- bind_rows(str_tdf %>% 
                         dplyr::select(type, gross_revenue) %>%
                         dplyr::mutate(tenure = 'str'),
                       ltr_tdf %>%
                         dplyr::select(type, gross_revenue) %>%
                         dplyr::mutate(tenure = 'ltr'))

   revdens <- ggplot(rev_df, 
                     aes(x=gross_revenue, fill=tenure, color=tenure)) +
    geom_density(alpha=.5) +
    scale_fill_manual(values=c(ltr_col, str_col)) +
    scale_color_manual(values=c(ltr_col, str_col)) +
    ggtitle('Annual Revenues by Tenure Type') +
    xlab('Annual Revenue') +
    scale_x_continuous(breaks=c(seq(0,60000, by=20000)),
                       labels=c('$0', '$20,000', '$40,000', '$60,000'))+
    theme(legend.position='bottom',
          legend.title = element_blank(),
          plot.title = element_text(hjust = 0.5),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.title.y=element_blank()) +
    coord_cartesian(xlim=c(0, 70000))

@@

   prevdens <- ggplot(prev_df, 
                     aes(x=gross_revenue, fill=tenure, color=tenure)) +
    geom_density(alpha=.5) +
    scale_fill_manual(values=c(ltr_col, str_col)) +
    scale_color_manual(values=c(ltr_col, str_col)) +
    ggtitle('Annual Revenues by Tenure Type') +
    xlab('Annual Revenue') +
    scale_x_continuous(breaks=c(seq(0,60000, by=20000)),
                       labels=c('$0', '$20,000', '$40,000', '$60,000'))+
    theme(legend.position='bottom',
          legend.title = element_blank(),
          plot.title = element_text(hjust = 0.5),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.title.y=element_blank()) +
    coord_cartesian(xlim=c(0, 70000))

@@

@@

```{r locationmaps.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}

 # Set submarket colors
   # Make map
  tm_shape(sub_sf) +
    tm_polygons() + 
  tm_shape(study_area) + 
    tm_polygons(col='dodgerblue3') +
  tm_shape(ltr_sf) +
    tm_symbols(size=.05, col='black', border.alpha=0, alpha=.02, shape=15)

  tm_shape(sub_sf) +
    tm_polygons() + 
  tm_shape(study_area) + 
    tm_polygons(col='dodgerblue3') +
  tm_shape(str_sf) +
    tm_symbols(size=.05, col='black', border.alpha=0, alpha=.2, shape=15)

  str_map <- ggplot() +
     geom_polygon(data=ssub_sf, aes(x=long, y=lat, group=group), fill='white', color='grey70') +
#     geom_point(data=str_df, aes(x=longitude, y=latitude, color=geo.mrkt), size=.2,
#                alpha=.2) +
#     scale_color_manual(values=sm_col) +
#     scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
#     scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
#     xlab('') + ylab('')+
#     theme(legend.position = 'bottom',
#           legend.title = element_blank(),
#           plot.title = element_text(hjust = 0.5),
#           panel.grid.major = element_blank(),
#           panel.grid.minor = element_blank(),
#           panel.background = element_rect(fill = "white"),
#           axis.text.x = element_blank(),
#           axis.text.y = element_blank(),
#           axis.ticks = element_blank(),
#           axis.title.x=element_blank(),
#           axis.title.y=element_blank(),
#           panel.border = element_rect(colour = "black", fill=NA, size=1)) +
#     guides(colour = guide_legend(override.aes = list(size=3,
#                                                      alpha=1))) + 
#     ggtitle('Short-Term Rental Locations')+
#     theme(plot.title = element_text(hjust = 0.5))
#   
# ```
# 
# ```{r ltr.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
# 
#   # Make map
# 
#   ltr.map <- ggplot() +
#     geom_polygon(data=subs, aes(x=long, y=lat, group=group), fill='white', color='grey70') +
#     geom_point(data=ltr_df, aes(x=longitude, y=latitude, color=geo.mrkt), size=.1,
#                alpha=.1) +
#     scale_color_manual(values=sm_col) +
#     scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
#     scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
#     xlab('') + ylab('')+
#     theme(legend.position = 'bottom',
#           legend.title = element_blank(),
#           plot.title = element_text(hjust = 0.5),
#           panel.grid.major = element_blank(),
#           panel.grid.minor = element_blank(),
#           panel.background = element_rect(fill = "white"),
#           axis.text.x = element_blank(),
#           axis.text.y = element_blank(),
#           axis.ticks = element_blank(),
#           axis.title.x=element_blank(),
#           axis.title.y=element_blank(),
#           panel.border = element_rect(colour = "black", fill=NA, size=1)) +
#     guides(colour = guide_legend(override.aes = list(size=3,
#                                                      alpha=1))) + 
#     ggtitle('Long-Term Rental Locations')+
#     theme(plot.title = element_text(hjust = 0.5))
#   
# ```
# 
# ```{r loc.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.width=9}
#   
#   png(file=paste0(fig.path, 'str_locmap.png'), width = 680, height = 590, 
#       bg='transparent')
#      str.map
#   dev.off()
#   
#   png(file=paste0(fig.path, 'ltr_locmap.png'), width = 680, height = 590, 
#       bg='transparent')
#      ltr.map
#   dev.off()
# 
#   ggMultiPlots(str.map, ltr.map, cols=2)
#   
#   save(str.map, file=paste0(fig.path, 'strMap.RData'))
#   save(ltr.map, file=paste0(fig.path, 'ltrMap.RData'))
# 
# 
# ```
# 
# The chart below break down the relative frequency of short and long term rental properties across the five submarkets. 
# 
```{r smtype.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.width=9}
